Copulas and their potential for ecology

### 2019-12-19 Paper.Rmd
what to do about the notation table

We give a brief introduction to copulas, focusing, for simplicity, on bivariate 
copulas and on concepts needed
for the rest of the paper. We assume familiarity with the basic 
language of probability distributions and random variables.
See @nelsen2006_copula, @Genest2007, @joe2014_dependence, and
@MaiScherer2017 for general background on copulas, 
and see also @Anderson2018, part of 
which is a short introduction to 
copulas for ecologists. A bivariate *copula* can be defined as a bivariate cdf 
with both margins uniform on $(0,1)$ (@joe2014_dependence, p. 7). 
This will be the 
cdf of a bivariate random variable with uniform marginals, and 
the terminology *copula* is sometimes also applied to this random vector. 
A foundational theorem of
@sklar1959_theorem (see also @MaiScherer2017, p. 16) 
says that if $F$ is the cdf
of a random vector $(X,Y)$, with margins $F_X$ and $F_Y$, then there 
exists a copula $C$
such that for all $(x,y)$ in the Euclidean plane, $F(x,y)=C(F_X(x),F_Y(y))$.
The theorem also says $C$ is unique if $F_X$ and $F_Y$ are continuous.
Thus $C$ couples the bivariate cdf, $F$, with the 
cdfs of the marginals. 
Finally, Sklar's theorem says that if $D$ is any bivariate copula and 
$G_A$ and $G_B$ are univariate cdfs, then 
$D(G_A(x),G_B(y))$ is a valid cdf 
of some bivariate random variable.
The applications of this study fall within the case in which univariate marginal 
distributions have continuous, strictly 
monotonic cdfs, and this case is simpler. So we 
henceforth make such an assumption.

>>>>

We give a brief introduction to copulas, focusing, for simplicity, on bivariate 
copulas and on concepts needed
for the rest of the paper. We assume familiarity with the basic 
language of probability distributions and random variables.
See @nelsen2006_copula, @Genest2007, @joe2014_dependence, and
@MaiScherer2017 for general background on copulas, 
and see also @Anderson2018, part of 
which is a short introduction to 
copulas for ecologists. A bivariate *copula* can be defined as a bivariate cdf 
with both margins uniform on $(0,1)$ (@joe2014_dependence, p. 7). 
This will be the 
cdf of a bivariate random variable with uniform marginals, and 
the terminology *copula* is sometimes also applied to this random vector. 
A foundational theorem of
@sklar1959_theorem (see also @MaiScherer2017, p. 16) 
says that if $F$ is the cdf
of a random vector $(X,Y)$, with margins $F_X$ and $F_Y$, then there 
exists a copula $C$
such that for all $(x,y)$ in the Euclidean plane, $F(x,y)=C(F_X(x),F_Y(y))$.
The theorem also says $C$ is unique if $F_X$ and $F_Y$ are continuous.
Thus $C$ couples the bivariate cdf, $F$, with the 
cdfs of the marginals. 
Finally, Sklar's theorem says that if $D$ is any bivariate copula and 
$G_A$ and $G_B$ are univariate cdfs, then 
$D(G_A(x),G_B(y))$ is a valid cdf 
of some bivariate random variable.
The applications of this study fall within the case in which univariate marginal 
distributions have continuous, strictly 
monotonic cdfs, and this case is simpler. So we 
henceforth make such an assumption. Table SX provides a summary
of notation.
<!--***DAN: Shyamolina, once I email you an edited version of the
table you produced, please make a table in the sup mat Rmd and cause it to be
cited here in place of the SX above. Please place the table in such
a way that SX is replaced with S1,  since I believe this is now going
to be the first supplementary table we are citing.-->
